Model LF

### 2023-03-13 paper version Hamid test.Rmd
Commit

COMMENT> 
IDENTITY> pconk_ds
EQ> pconk_ds= pconk_ds_used
if> disc <= 0
IDENTITY> pconk_ds
EQ> pconk_ds= pconk_ds_disc
if> disc > 0

@@

shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

```{r}
# Define add-factor list (defining shock)
constantAdjList_3 <- list(
 shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)

@@

## Sens IR LF

@@

shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)

@@

plot(window((ur_ds_01 - ur_ds_bs1)*100, start= 2014), col= "blue", xlab= "Year", ylab= "percentage change", main= "Scenario 1", ylim= c(-0.03,0.02));
lines(window(((yk_ds_01 - yk_ds_bs1) / yk_ds_bs1)*100, start= 2014), col= "green");
legend("left", legend=c("Unemployment rate","GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

plot(window(AD_01 - AD_bs1, start= 2014), col= "blue", xlab= "Year", ylab= "Level change", main= "Scenario 1");
lines(window(TB_01 - TB_bs1, start= 2014), col= "green");
legend("left", legend=c("Aggregate demand","Trade balance"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

```{r}
plot(window(nl_g_01 - nl_g_bs1, start= 2014), col= "blue", xlab= "Year", ylab= "Level change", main= "Scenario 1");
legend("left", legend=c("Governmnet net lending"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```

@@

plot(window((ur_ds_02 - ur_ds_bs2)*100, start= 2014), col= "blue", xlab= "Year", ylab= "percentage change", main= "Scenario 2", ylim= c(-0.03,0.03));
lines(window(((yk_ds_02 - yk_ds_bs2) / yk_ds_bs2)*100, start= 2014), col= "green");
legend("left", legend=c("Unemployment rate","GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

plot(window(AD_02 - AD_bs2, start= 2014), col= "blue", xlab= "Year", ylab= "Level change", main= "Scenario 2");
lines(window(TB_02 - TB_bs2, start= 2014), col= "green");
legend("left", legend=c("Aggregate demand","Trade balance"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

```{r}
plot(window(nl_g_02 - nl_g_bs2, start= 2014), col= "blue", xlab= "Year", ylab= "Level change", main= "Scenario 2");
legend("left", legend=c("Governmnet net lending"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```

@@

plot(window((ur_ds_03 - ur_ds_bs3)*100, start= 2014), col= "blue", xlab= "Year", ylab= "percentage change from baseline", main= "Scenario 3", ylim= c(-0.015,0.015));
lines(window(((yk_ds_03 - yk_ds_bs3) / yk_ds_bs3)*100, start= 2014), col= "green");
legend("left", legend=c("Unemployment rate","GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

plot(window(AD_03 - AD_bs3, start= 2014), col= "blue", xlab= "Year", ylab= "Level change from Baseline", main= "Scenario 3", ylim= c(-50,110));
lines(window(TB_03 - TB_bs3, start= 2014), col= "green");
legend("left", legend=c("Aggregate demand","Trade balance"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

```{r}
plot(window(nl_g_03 - nl_g_bs3, start= 2014), col= "blue", xlab= "Year", ylab= "Level change from baseline", main= "Scenario 3");
legend("left", legend=c("Governmnet net lending"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```

plot(window((ur_ds_04 - ur_ds_bs4)*100, start= 2014), col= "blue", xlab= "Year", ylab= "percentage change from baseline", main= "Scenario 4", ylim= c(-0.03,0.03));
lines(window(((yk_ds_04 - yk_ds_bs4) / yk_ds_bs4)*100, start= 2014), col= "green");
legend("left", legend=c("Unemployment rate","GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

plot(window(AD_04 - AD_bs4, start= 2014), col= "blue", xlab= "Year", ylab= "Level change from baseline", main= "Scenario 4");
lines(window(TB_04 - TB_bs4, start= 2014), col= "green");
legend("left", legend=c("Aggregate demand","Trade balance"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

```{r}
plot(window(nl_g_04 - nl_g_bs4, start= 2014), col= "blue", xlab= "Year", ylab= "Level change", main= "Scenario 4");
legend("left", legend=c("Governmnet net lending"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```

@@

plot(window((ur_ds_S1 - ur_ds_S1_base)*100, start= 2014), col= "blue", xlab= "Year", ylab= "percentage change from baseline", main= "Sensitivity 1", ylim= c(-0.03,0.03));
lines(window(((yk_ds_S1 - yk_ds_S1_base) / yk_ds_S1_base)*100, start= 2014), col= "green");
legend("left", legend=c("Unemployment rate","GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

plot(window(AD_S1 - AD_S1_base, start= 2014), col= "blue", xlab= "Year", ylab= "Level change from baseline", main= "Sensitivity 1");
lines(window(TB_S1 - TB_S1_base, start= 2014), col= "green");
legend("left", legend=c("Aggregate demand","Trade balance"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

```{r}
plot(window(nl_g_S1 - nl_g_S1_base, start= 2014), col= "blue", xlab= "Year", ylab= "Level change", main= "Sensitivity 1");
legend("left", legend=c("Governmnet net lending"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```

@@

plot(window((ur_ds_S2 - ur_ds_S2_base)*100, start= 2014), col= "blue", xlab= "Year", ylab= "percentage change from baseline", main= "Sensitivity 2", ylim= c(-0.015,0.015));
lines(window(((yk_ds_S2 - yk_ds_S2_base) / yk_ds_S2_base)*100, start= 2014), col= "green");
legend("left", legend=c("Unemployment rate","GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

plot(window(AD_S2 - AD_S2_base, start= 2014), col= "blue", xlab= "Year", ylab= "Level change from baseline", main= "Sensitivity 2", ylim= c(-50,100));
lines(window(TB_S2 - TB_S2_base, start= 2014), col= "green");
legend("left", legend=c("Aggregate demand","Trade balance"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

```{r}
plot(window(nl_g_S2 - nl_g_S2_base, start= 2014), col= "blue", xlab= "Year", ylab= "Level change", main= "Sensitivity 2");
legend("left", legend=c("Governmnet net lending"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```

>>>>

COMMENT> 
IDENTITY> pconk_ds
EQ> pconk_ds= pconk_ds_disc

@@

shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)

@@

shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

```{r}
# Define add-factor list (defining shock)
constantAdjList_3 <- list(
 shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)

@@

## Sens IR

@@

shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
shock_lf_model = TIMESERIES(shock_lf_model_shock+1 ,START=c(2006,3),  FREQ='Q')
)

@@

plot(window((ur_ds_01 - ur_ds_bs1)*100, start= 2014), col= "blue", lwd=2, ylab= "percentage change", main= "Scenario 1", ylim= c(-0.03,0.02));
lines(window(((yk_ds_01 - yk_ds_bs1) / yk_ds_bs1)*100, start= 2014), col= "green", lwd=2);
legend("left", legend=c("Unemployment rate","GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

plot(window(AD_01 - AD_bs1, start= 2014), col= "blue", lwd=2, ylab= "Level change", main= "Scenario 1", ylim= c(-100,100));
lines(window(TB_01 - TB_bs1, start= 2014), col= "green", lwd=2);
legend("top", legend=c("Aggregate demand","Trade balance"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

```{r}
plot(window(nl_g_01 - nl_g_bs1, start= 2014), col= "blue", lwd=2, ylab= "Level change", main= "Scenario 1");
legend("left", legend=c("Governmnet net lending"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```

@@

plot(window((ur_ds_02 - ur_ds_bs2)*100, start= 2014), col= "blue", lwd=2, ylab= "percentage change", main= "Scenario 2", ylim= c(-0.02,0.02));
lines(window(((yk_ds_02 - yk_ds_bs2) / yk_ds_bs2)*100, start= 2014), col= "green", lwd=2);
legend("top", legend=c("Unemployment rate","GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

plot(window(AD_02 - AD_bs2, start= 2014), col= "blue", xlab= "Year", lwd=2, ylab= "Level change", main= "Scenario 2", ylim=c(-100,100));
lines(window(TB_02 - TB_bs2, start= 2014), col= "green", lwd=2);
legend("top", legend=c("Aggregate demand","Trade balance"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

```{r}
plot(window(nl_g_02 - nl_g_bs2, start= 2014), col= "blue", lwd=2, ylab= "Level change", main= "Scenario 2");
legend("left", legend=c("Governmnet net lending"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```

@@

plot(window((ur_ds_03 - ur_ds_bs3)*100, start= 2014), col= "blue", lwd=2, ylab= "percentage change from baseline", main= "Scenario 3", ylim= c(-0.015,0.015));
lines(window(((yk_ds_03 - yk_ds_bs3) / yk_ds_bs3)*100, start= 2014), col= "green", lwd=2);
legend("top", legend=c("Unemployment rate","GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

plot(window(AD_03 - AD_bs3, start= 2014), col= "blue", lwd=2, ylab= "Level change from Baseline", main= "Scenario 3", ylim= c(-50,110));
lines(window(TB_03 - TB_bs3, start= 2014), col= "green", lwd=2);
legend("top", legend=c("Aggregate demand","Trade balance"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

```{r}
plot(window(nl_g_03 - nl_g_bs3, start= 2014), col= "blue", lwd=2, ylab= "Level change from baseline", main= "Scenario 3");
legend("left", legend=c("Governmnet net lending"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```

@@

plot(window((ur_ds_S1 - ur_ds_S1_base)*100, start= 2014), col= "blue", lwd=2, ylab= "percentage change from baseline", main= "Sensitivity 1", ylim= c(-0.03,0.03));
lines(window(((yk_ds_S1 - yk_ds_S1_base) / yk_ds_S1_base)*100, start= 2014), col= "green", lwd=2);
legend("top", legend=c("Unemployment rate","GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

plot(window(AD_S1 - AD_S1_base, start= 2014), col= "blue", lwd=2, ylab= "Level change from baseline", main= "Sensitivity 1");
lines(window(TB_S1 - TB_S1_base, start= 2014), col= "green", lwd=2);
legend("left", legend=c("Aggregate demand","Trade balance"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

```{r}
plot(window(nl_g_S1 - nl_g_S1_base, start= 2014), col= "blue", lwd=2, ylab= "Level change", main= "Sensitivity 1");
legend("left", legend=c("Governmnet net lending"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```

@@

plot(window((ur_ds_S2 - ur_ds_S2_base)*100, start= 2014), col= "blue", lwd=2, ylab= "percentage change from baseline", main= "Sensitivity 2", ylim= c(-0.015,0.015));
lines(window(((yk_ds_S2 - yk_ds_S2_base) / yk_ds_S2_base)*100, start= 2014), col= "green", lwd=2);
legend("top", legend=c("Unemployment rate","GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

plot(window(AD_S2 - AD_S2_base, start= 2014), col= "blue", lwd=2, ylab= "Level change from baseline", main= "Sensitivity 2", ylim= c(-50,100));
lines(window(TB_S2 - TB_S2_base, start= 2014), col= "green", lwd=2);
legend("left", legend=c("Aggregate demand","Trade balance"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()

```{r}
plot(window(nl_g_S2 - nl_g_S2_base, start= 2014), col= "blue", lwd=2, ylab= "Level change", main= "Sensitivity 2");
legend("left", legend=c("Governmnet net lending"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green"));
grid()
```
